Verifying Demonstrations

### 2017-08-23 SystemModel.tex
Updates def of proofs, adds dependency tree

\begin{definition}[Participation proof]
  A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; \sigma)\), 
  where
  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest}.
  \(\sigma\) is a signature vouching for participation.
\end{definition}

\begin{frame}
  \mode<presentation>{%
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
          \sigma)\), where
      \item \(id, t_s, t_e, x, y\) are as before.
      \item \(\sigma\) is a signature vouching for participation.
    \end{itemize}
  \end{definition}

@@

>>>>

\begin{definition}[Participation proof]
  A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; \sigma)\), where
  \(id, t_s, t_e\) are as in \cref{DefProtest},
  \(lp\) is a location proof and
  \(\sigma\) is a signature over the proof.
\end{definition}

\begin{frame}
  \mode<presentation>{%
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; 
          \sigma)\), where
      \item \(id, t_s, t_e\) are as before,
      \item \(lp\) is a location proof and
      \item \(\sigma\) is a signature over the proof.
    \end{itemize}
  \end{definition}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=right,level distance=5em}
    \Tree [.Proof
      [.{wsig} {\(x,y\)} [.{osig} [.{\(id\)} manifesto ] head ] [.tsig head'' ] ]
      {\dots}
      [.{wsig} {\dots} ]
    ]
  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the blockchain.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnesses by a trusted witness (tsig).
    }
  }
\end{figure}
\end{frame}
